\documentclass[a4paper,12pt]{report}


\usepackage[paper=A4,pagesize]{typearea}
\usepackage{listings}
\usepackage{afterpage}
\usepackage{siunitx}
\usepackage{url}
\usepackage{graphicx}
\usepackage{pdflscape}
\usepackage{lmodern,textcomp}
\usepackage{longtable}
\usepackage{adjustbox}
\usepackage{pdflscape}
\usepackage[square,numbers]{natbib}
\usepackage{notoccite}
\usepackage{chapterbib, tabularx}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage[euler]{textgreek}
\usepackage[center]{caption}
\usepackage{acronym}
\usepackage{xr}
\usepackage[dvipsnames]{xcolor}
\usepackage{float}
\usepackage{setspace}
\DeclareUnicodeCharacter{2005}{ }
\DeclareUnicodeCharacter{2606}{ }
\DeclareUnicodeCharacter{2212}{ }
\DeclareUnicodeCharacter{E5F8}{ }


\newcolumntype{C}[1]{>{\centering\arraybackslash}p{#1}}

\externaldocument[lit-]{Chapter2/ch2}
\externaldocument[exp-]{Experimental/ch1}
\externaldocument[dft-]{Chapter3/ch3}
\externaldocument[proc-]{Chapter4/ch4}
\externaldocument[HRS-]{Chapter5/ch5}




\newcolumntype{L}{>{\centering\arraybackslash}m{3cm}}
\doublespacing
\begin{document}

\begin{titlepage}
	\centering
	{\scshape\Large Imperial College London \par}
	{\scshape\Large Department of Chemical Engineering\par}
	\vspace{1.5cm}
	{\LARGE\bfseries Developing a Hydrogen Impurity Enrichment Device for Measuring Impurities in Fuel-Grade Hydrogen\par}
	\vspace{2cm}
	{\Large Marc Plunkett\par}
	\vfill
	A thesis presented for the degree of Doctor of Philosophy\par

	\vfill

% Bottom of the page
	{\large \today\par}
\end{titlepage}



\chapter*{Declaration of Originality}
I hereby declare that the work reported in this thesis was composed and originated entirely by me. Information derived from published and unpublished results of others has been acknowledged in the text and in the relevant references included within the thesis.

\noindent\newline
\textbf{Marc Plunkett}\newline
\noindent
September, 2020\newline
\noindent
\\
\\
\\
\\
\\
\\

The copyright of this thesis rests with the author and is made available under a 'Creative Commons Attribution Non-Commercial No Derivatives' licence. Researchers are free to copy, distribute or transmit the thesis on the condition that they attribute it, that they do not use it for commercial purposes and that they do not alter, transform or build upon it. For any reuse or redistribution, researchers must make clear to others the licence terms of this work.

\chapter*{Executive summary}
As government entities around the world seek to further develop their hydrogen economies with the aim of reducing their CO\textsubscript{2} emissions from the transport sector further adoption of fuel cell electric vehicles is expected. This thesis focused on developing a hydrogen impurity enrichment device using an optimised palladium based membrane as a method for low cost measurement of impurities to ISO 14687 standards. The composition of the palladium membrane was first optimised by screening of compositions using density functional theory. Compositions are simulated by placing ISO 14687 impurities on the surface and measuring their final energy level, with compositions which have a lower energy level with the impurity being deemed unsuitable. The best membrane compositions were then fabricated using a number of thin film deposition techniques including electroless plating and magnetron sputtering. The resulting micron thick palladium membranes were then subjected to two varieties of hydrogen impurities, carbonaceous and sulphurous, and  their reactivity measured by using XPS and the change in hydrogen permeability when subjected to impurities. The result from this was that PdCuZr membranes were the least reactive and therefore the most suitable for hydrogen impurity enrichment where a membrane with low reactivity to impurities is required. Finally the resulting membrane was tested in an improved hydrogen impurity enrichment device which was set up with improved process control systems. The membrane was benchmarked against a commercial PdAgAu membrane and tested using an inert sample, sulphurous sample and for the first time a sample taken from a hydrogen refuelling station.

\chapter*{Acknowledgements}
Throughout the writing of this dissertation I have received a great deal of support and assistance. I  would  first  like  to  thank  my  supervisors,  Dr.  A.  Murugan and Prof. K. Li, whose insights and knowledge into the subject matter steered me through this research.

I would like to acknowledge my colleagues from my National Physical Laboratory and Imperial College London for their wonderful collaboration. You supported me greatly and were always willing to help me. I would particularly like to thank Dr. B. Wang and Dr. T. Li at Imperial College and Dr. T. Bacquart, Dr. S. Bartlett and Ms. A. Morris, and Ms. N. Moore at National Physical Laboratory. I want to thank you for your excellent guidance and  for  taking the time to teach me the techniques, methodologies and providing  me  with  the  tools  that I  needed  to  choose  the  right  direction  and  successfully complete my dissertation.

And my biggest thanks to my friends and family for all the support you have shown me through this research. I would like to thank my brother, David, for his wise counsel and sympathetic ear and my parents who  are always there for me. Finally, there are my dear friends; Dr. Iain Hyndman, Emma Abraham, David Mckechnie, Bradley Hannah, Anthony Houghton, and Chen Chen for seeing me through the highs and lows and for creating so many unforgettable moments outside of my research. 



\listoffigures
\listoftables

\include{acronyms}

\tableofcontents


\include{Chapter1/ch1}

\include{Chapter2/ch2}

\include{Experimental/ch1}

\include{Chapter3/ch3}

\include{Chapter4/ch4}

\include{Chapter5/ch5}

\include{enrichmentresults/ch5}

\include{Chapter6/ch6}

\include{appendices/master}

\chapter*{List of Publications and Presentations}

\section*{Publications}
\begin{enumerate}
    \item \textbf{M. Plunkett}, K.Li, A. Murugan; Review of membrane technologies for hydrogen impurity enrichment (To be resubmitted)
    \item \textbf{M. Plunkett}, A. Morris, S. Nayebossardi, T. Bacquart, B. Wang,  S. Spencer, K. Mingard, K. Li, A. Murugan ; Determining impurity resistant palladium alloy membrane compositions for enrichment of hydrogen fuel samples with low level contaminants (In final preparation)
    \item \textbf{M. Plunkett}, N. Moore, T. Bacquart, K.Li, A. Murugan; Analysing low level impurities in hydrogen refuelling station hydrogen using hydrogen impurity enrichment; (In preparation)

\end{enumerate}

\section*{Oral Presentations}
\begin{enumerate}
    \item \textbf{M. Plunkett}, A. Murugan, K. Li; A hydrogen impurity enrichment device using Pd-Alloy membranes to support the hydrogen economy. Presented at International Conference for Membrane and Electromembrane Processes 2018, 13th – 16th May 2018, Prague, Czech Republic.
    \item \textbf{M. Plunkett}, A. Murugan, K. Li; A hydrogen impurity enrichment device using Pd-Alloy membranes to support the hydrogen economy. Presented at 15th International Conference on Inorganic Membranes, 18th – 22nd June 2018, Dresden, Germany. 
    \item \textbf{M. Plunkett}; Determining impurity resistant palladium alloy membrane compositions for enrichment of hydrogen fuel samples with low level ISO 14687-2 contaminants. Presented at 2nd bi-annual Gas and Particle Metrology symposium, 14th August, 2018, Teddington, United Kingdom 
    \item \textbf{M. Plunkett}; Developing suitable palladium alloy membranes for enrichment of hydrogen fuel samples to satisfy growing analytical demand. Presented at H2FC Research Conference University of Birmingham, 14th August, 2018, Birmingham, United Kingdom 
    \item \textbf{M. Plunkett}; Hydrogen Quality Assurance Work Package 2, Task 2.4: Optimisation of impurity enrichment devices. EMPIR MetroHyVe M39 meeting, 25th August, 2020, Online 
\end{enumerate}


\end{document}